---
title: "Exercise Cleaning Data on R"
author: "Maulana Mirza E"
date: "11/10/2021"
output: html_document
---

Load Data
```{r}
library(tidyverse)
library(lubridate)
df <- read_csv("https://raw.githubusercontent.com/dioariadi/dibimbing/main/data_cleansing_raw%20-%20Sheet1.csv")
df
```
There are several ways, this is one way to solve it.
Problem 1 - check 'na' in TotalCharge column and changed to 'NA', Fix MonthlyCharges column, Fix TotalCharge to numeric form
```{r}
# na check
df$TotalCharges
is.na(df$TotalCharges)
df %>% distinct(TotalCharges)
```
```{r}
# na to NA
df <- df %>%
  mutate(TotalCharges = replace(TotalCharges, TotalCharges == "na", NA),
         TotalCharges = replace(TotalCharges, TotalCharges == "N/A", NA),
         TotalCharges = as.numeric(TotalCharges))
is.na(df$TotalCharges)

df %>% glimpse()
```
```{r}
# Fix MonthlyCharges column
df <- df %>% mutate(MonthlyCharges=replace(MonthlyCharges,is.nan(MonthlyCharges)==TRUE,NA))
```
```{r}
# Fix TotalCharge column to numeric form
df %>% 
  mutate(TotalCharges=as.numeric(TotalCharges)) %>% 
  pull(TotalCharges)
```
Problem 2 - Fix PaymentMethod column
```{r}
# PaymentMethod Checked
df %>% distinct(PaymentMethod)
is.na(df$PaymentMethod)
```
```{r}
# PaymentMethod Fixed - values "--" to NA
df <- df %>%
  mutate(PaymentMethod = replace(PaymentMethod, PaymentMethod ==  "--", NA))
is.na(df$PaymentMethod)
df$PaymentMethod
```
Problem 3 - Fixing date format
```{r}
# LastTransactionDate Checked
df %>% distinct(LastTransactionDate)
```
```{r}
# LastTransactionDate Fixed
df <- df %>%
  mutate(LastTransactionDate=ymd(LastTransactionDate)) 

df %>% select(LastTransactionDate)
```
Problem 4 - Fixing customerID columns (split the values)
```{r}
# customerID Checked
df %>% distinct(customerID)
```
```{r} 
# Split customerID
df %>% separate(col = customerID,into = c("customerID","uniqueCode"))

df <- df %>% 
  separate(col = customerID,into = c("customerID","uniqueCode"))
```
Problem 5 -Change the churn column no/yes to integer 1/0
```{r}
df %>% 
  mutate(Churn=if_else(Churn=="yes",1,0)) %>% 
  select(Churn)

df <- df %>% 
  mutate(Churn=if_else(Churn=="yes",1,0))
```
Problem 6 - Finishing df
```{r}
# Remove all values of na in data
df %>% na.omit()
```
```{r}
# Finishing
df <- df %>%
  mutate(TotalCharges = replace(TotalCharges,
                                is.na(TotalCharges),
                                median(TotalCharges, na.rm = T)),
         MonthlyCharges = replace(MonthlyCharges,
                                is.na(MonthlyCharges),
                                median(MonthlyCharges, na.rm = T)),
         PaymentMethod= replace(PaymentMethod,is.na(PaymentMethod)==TRUE,"Unavailable"),
         LastTransactionDate = replace(LastTransactionDate,
                                is.na(LastTransactionDate),
                                mean(LastTransactionDate, na.rm = T)))
df
```

